Milestone 4

### 2020-01-06 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Adding in validation dataset. Serializing everything based upon version (i.e., each version gets its own suite of tables).

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/modeling.R')
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(bigrquery)
library(DBI)
library(lubridate)
```

# tl;dr 
This notebook generates the training (Version N) and prediction (Version N+1) datasets, trains a statistical matching model, extracts a representative subset of Beta with respect to Release, and calculates the final Release Health Metrics as described in milestone 4 of this PRD[Release performance health metrics](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

# Dataset Preparation
The datasets are generated by this [notebook](
https://storage.cloud.google.com/moz-fx-data-bq-data-science-cdowhygelund/notebooks/jupyter/Beta_Release_Subsetting_Data_Preparation_GCP.ipynb
) on a Dataproc cluster. These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `ccd_subBeta_training` (Version N) and `ccd_subBeta_prerelease` (Version N+1).

@@

df_train <- load_df("ccd_subBeta_training")
df_predict <- load_df('ccd_subBeta_prerelease')
```

@@

```{r serialize_datasets}
# training datasets
train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
train_file_path <- file.path('data', train_file_name)
save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)

# final prelease subsetted dataset
prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
prerelease_file_path <- file.path('data', prerelease_file_name)
save(predictions, file = prerelease_file_path)
gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)

@@

* `r gcs_train_file_path`
* `r gcs_prerelease_file_path`
* `r gcs_release_health_file_path`

@@

@@

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = "ccd_subbeta_training_cleaned") %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = "ccd_subbeta_training_final") %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = "ccd_subbeta_prelease_cleaned") %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )

@@

Subsetted dataset
```{r bq_write_subset}
bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = "ccd_subbeta_prelease_subset") %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )
```

>>>>

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/modeling.R')
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(bigrquery)
library(DBI)
library(lubridate)
library(htmltab)
library(stringr)
```

# tl;dr 
This notebook generates the training (Version N), prediction (Version N+1), and validation (Version N) datasets, trains a statistical matching model, extracts a representative subset of Beta with respect to Release, and calculates the final Release Health Metrics as described in milestone 4 of this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

# Dataset Preparation
The datasets are generated by this [notebook](
https://storage.cloud.google.com/moz-fx-data-bq-data-science-cdowhygelund/notebooks/jupyter/subbeta_training_prediction_data_prep.ipynb
) on a Dataproc cluster. These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `ccd_subBeta_training_<version N>`, `ccd_subBeta_prerelease_<version N+1>`, and `ccd_subBeta_validation_<version N>`.

```{r version, echo=FALSE}
sched <- htmltab('https://wiki.mozilla.org/Release_Management/Calendar', which=2) %>%
  mutate('rel_dates' = ymd(sched$`Release Date`)) %>%
  mutate('version' = as.numeric(str_match(sched$Beta, 'Firefox ([0-9]+)')[,2])) %>%
  filter(rel_dates < now())

v_n1 <- sched$version[1]
v_n <- sched$version[2]
```

@@

df_train <- load_df(paste("ccd_subBeta_training", v_n, sep='_'))
df_predict <- load_df(paste('ccd_subBeta_prerelease'), v_n1, sep='_')
df_validate <- load_df(paste('ccd_subBeta_validation'), v_n, sep='_')
```

@@

```{r serialize_datasets}
# training datasets
# train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
train_file_name <- paste('df_train_', v_n, sep='_')
train_file_path <- file.path('data', train_file_name)
save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)

# final prelease subsetted dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
prerelease_file_name <- paste('df_prerelease_', v_n1, sep='_')
prerelease_file_path <- file.path('data', prerelease_file_name)
save(predictions, file = prerelease_file_path)
gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)

# validation dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
validation_file_name <- paste('df_validation_', v_n1, sep='_')
validation_file_path <- file.path('data', validation_file_name)
save(validation, file = validation_file_path)
gcs_validation_file_path <- file.path('data', 'milestone4', validation_file_name)

@@

* `r gcs_train_file_path`
* `r gcs_prerelease_file_path`
* `r gcs_validation_file_path`
* `r gcs_release_health_file_path`

@@

```{r gcp_validation_storage_push, warning=FALSE}
upload_try <- gcs_upload(validation_file_path, name = gcs_validation_file_path)
upload_try
```

@@

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = paste("ccd_subbeta_training_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = paste("ccd_subbeta_training_final", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_cleaned", v_n1, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_predict_f) )

@@

Subsetted dataset
```{r bq_write_subset}
bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_subset", v_n1, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )
```

Validation dataset
```{r bq_write_validate}
bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "validation",
         table   = paste("ccd_subbeta_validation_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )
```
